Expectations bias moral evaluations

### 2018-09-29 paper/paper-apa.Rmd
moved theoretical stuff to appendix

keywords          : "Evaluation; Moral judgment; Information theory"
wordcount         : "1911"

@@

From this it can be shown that the value assigned to event $S$ is proportional to its prior probability (see Theoretical Formalization section in supplemental materials). Specifically, it is the difference in the expected utility under different values of $S$, weighted by the inverse of the prior probability of $S$. [^1]

@@

# General Methods

@@

## Study 1

@@

### Results and discussion

@@

## Study 2

In Study 1 we found that people’s judgments of events were biased by their expectations about those events. When forced to choose between two events, participants decided that unexpected events were more upsetting than expected events. In Study 2, we sought to test our hypothesis using a more conservative method: we provided participants with a more expressive response scale so that if they viewed the events under consideration as equally harmful, their responses could reflect their attitude.

@@

### Materials and procedure {#s2-materials-procedure .unnumbered}

>>>>

keywords          : "Evaluation; Moral judgment; Information theory"
wordcount         : "3898 (total), 1988 (excluding methods and results)"

@@

From this it can be shown that the value assigned to event $S$ is proportional to its prior probability (see Appendix). Specifically, it is the difference in the expected utility under different values of $S$, weighted by the inverse of the prior probability of $S$. [^1]

@@

# General Method

@@

# Study 1

## Method

@@

## Results

@@

# Study 2

In Study 1 we found that people’s judgments of events were biased by their expectations about those events. When forced to choose between two events, participants decided that unexpected events were more upsetting than expected events. In Study 2, we sought to test our hypothesis using a more conservative method: we provided participants with a more expressive response scale so that if they viewed the events under consideration as equally harmful, their responses could reflect their attitude. 
## Method

## Participants

@@
